%
\subsection{Base Steps for Static Data Dependency and Dependency Quantity Analysis}
\label{sec:alg_weightedgegen}
\subsubsection{Vertices Estimation and Query Annotation Estimation}
\label{sec:alg_vertexgen}
The vertices in the static analysis dependency graph are actually identical as the  Execution-Based Dependency Graph, which are assigned variables in the program annotated with the unique label(line number). These vertices are collected by statically scanning the program, like what I do for vertices of its Execution-Based Dependency Graph. The vertices are defined formally as follows.

  \highlight{
\[
    \progV(c) \triangleq \left\{ 
  x^l \in \mathcal{LV} 
  ~ \middle\vert ~
  x^l \in \lvar_{c}
  \right\}
  \]
  }
  %

The static scanning of the programs also tells us whether one vertice(assigned variable) is assigned by a query request.  I have similar definition when defining the Execution-Based Dependency Graph, 
a set of pairs $\progF(c) \in \mathcal{P}(\mathcal{LV} \times \{0, 1\} )$ 
% is the set of pairs 
% The weight for each vertex in $\progV(c)$ is computed 
mapping each $x^l \in \progV(c)$ to a flag, either $0$ or $1$, where $1$  means $x^{l}$ is a member of $ \qvar_{c}$, a set of those variables assigned with query requests, and $0$ means $x^{l}$ not in this set. It is defined formally below.

\[\progF(c) =\left\{(x^l, n)  \in  \mathcal{LV} \times \{0, 1\} 
~ \middle\vert ~
x^l \in \lvar_{c},
n = 1 \iff x^l \in \qvar_{c} \land n = 0 \iff  x^l \not\in \qvar_{c} .
\right\}\]
%
\subsubsection{Abstract Execution Control Flow graph}
Since the edges of the execution-based graph of a program relies on the dependency relation, which handles both control flow and data flow, as an over-approximation of this graph, the edges of our static anlaysis dependency graph also covers these two kind of flows.  I develop a feasible data flow relation to catch these two flows, in Section~\ref{sec:alg_edgegen}.
%
The weight of every vertice in the execution-based graph is built on all possible execution traces.
In order to over-approximate the weight statically but still tightly, I present a symbolic reachability bound analysis for estimation of the weight of each vertice(label) in Section~\ref{sec:alg_weightgen},
in spirit of some reachablility bound techiniques.


The edges and weight estimation are both performed on basis of an abstract control flow graph of the program, I first show how to generate this abstract execution control flow graph before the introduction of  the edge and weight estimation.  
\label{sec:abscfg}
 I discuss the vertices and edge of the
abstract control flow graph for a program $c$, $\absG(c)$.

Every 
vertex corresponds to the unique
label.
Specifically,
the vertices of this graph is the set of $c$'s labels with an exit label $l_{ex}$, 
\[ 
  \absV(c) = labels(c)\cup\{l_{ex}\}
  \]
%  corresponding to a label command in the program.

% \wq{
  The edge in the abstract control flow graph comes from the abstract execution trace of the program. 
  The abstract execution trace, an abstract representation of the execution, consists of a list of abstract transitions. 
  Then, every abstract transition in the abstraction execution trace corresponds to an edge in the abstract control flow graph. In another word, the edge $(l_1, dc, l_2)$ in the abstract control flow graph, represents an abstract transition 
 from $l_1$ to $l_2$, with a set of difference constraints $dc$. 
 Also notice, the difference constraints generated during the abstract transition appears in the edge as annotation.
%  }

% over program's abstract execution 


% \wq{
  Overall, the vertices can be easily collected and the key point of construction of the abstract execution control flow graph for a program is the abstract execution trace, 
  which relies on the abstraction of expression and abstract transition (we also call it abstract event), I will discuss in the following section.
   To make it easy to understand, abstract control flow graph is a control flow graph, with difference constraints on every edge.
  % }  

%
\paragraph*{Expression Abstraction}

The expression assigned to the variable on the left hand of the assignment command is abstracted to an abstract value: (adopted from the expression abstraction method in paper \cite{sinn2017complexity}). The abstract value is expressed in the form of Difference constraint, denotated as $DC : \mathcal{VAR} \cup \constdom \to \mathcal{\mathcal{VAR} \times (\mathcal{VAR} \cup \constdom) } \times (\mathbb{Z} \cup \{\infty\})$.  $\constdom$ is called the Symbolic Constant defined as $\constdom \triangleq \mathbb{N} \cup \inpvar \cup \{\max{(\dbdom)}\} $, which consists of 
natural numbers $\mathbb{N}$,
the program's input variables $\inpvar$  
and a constant value $\max(\dbdom)$ for estimating the upper bound of variables which are
assigned by queries. 

Give an instance of difference constraint used here,
$DC(\mathcal{VAR}  \cup \constdom) \cup \{\top\}$ represents all the difference constraints over 
variable and symbolic constants. 
% The difference constraint $DC$ over $\mathcal{VAR} \cup \constdom$ 
It is a set of the inequality of form $x \leq y + v$ where $x \in \mathcal{VAR} $, 
$y \in \mathcal{VAR}  \cup \constdom$ and $v \in \mathbb{Z}$. 
This difference constraint is defined in the same way as
\cite{sinn2017complexity}. For concise, I use $\dcdom^{\top}$ to represent the $DC(\mathcal{VAR}  \cup \constdom) \cup \{\top\}$ .


 I show the expression abstraction $\absexpr : \expr \to \mathcal{VAR} \to DC(\mathcal{VAR}  \cup \constdom) \cup \{\top\} $ below.

%  I introduce the following notations and operations first
% % an expression abstraction method based on the expression abstraction in paper \cite{sinn2017complexity}.
% \\
% % is enriched into $\constdom \triangleq \mathbb{N} \cup \inpvar \cup \{\max{(\dbdom)}\} $.
% T
% \\

% represents the set of inequality over all $\mathcal{VAR}  \cup \constdom$. 

% The symbolic constant is enriched into $\constdom \triangleq \mathbb{N} \cup \inpvar \cup \{\max{(\dbdom)}\} $.
% It consists of 
% natural number $\mathbb{N}$,
% the symbolic constants $\inpvar$ (i.e., the set of the program's input variables), 
% and a constant value $\max(\dbdom)$ for estimating the upper bound of variables which are
% assigned by queries.
% \\
% The symbolic constant is enriched into $\constdom \triangleq \mathbb{N} \cup \inpvar \cup \{\max{(\dbdom)}\} $.
% \\

% % $ \absdom: \mathcal{P}(DC(\mathcal{VAR}  \cup \constdom) \cup \{\top \})$:
% \\
% $\constdom: \mathbb{N} \cup \inpvar \cup \{\max{(\dbdom)}\} $ 
% The  constant 
% \\
% % $DC(\mathcal{VAR}  \cup \constdom)$ represents the set of inequality over all $\mathcal{VAR}  \cup \constdom$.
% \\

% \[
%   \begin{array}{ll} 
%     \absexpr(y + c, x)  = x' \leq y + c  & c \in \mathbb{N} \land y \in (VAR \cup \constdom) \\
%     \absexpr(y - c, x)  = x' \leq y - c  & c \in \mathbb{N} \land y \in (VAR \cup \constdom) \\
%     \absexpr(v, x)  = x' \leq v + 0  & v \in (VAR \cup \constdom) \\
%     \absexpr(\aexpr, x) = x' \leq 0 + \infty   & \aexpr \text{ doesn't have any of the forms as above} \\
%     \absexpr(\qexpr, x)  = x' \leq 0 + \max(\dbdom) & \qexpr \text{ is a query expression}  \\
%     \absexpr(\bexpr, x) = x' \leq 0 + 1   & \bexpr \text{ is a boolean expression} \\
%   \end{array}
%   \]
  \[
    \begin{array}{ll} 
      \absexpr(x - v, x)  = x' \leq x - v  & x \in \grdvar \land v \in \mathbb{N} \\
      \absexpr(y + v, x)  = x' \leq y + v  & x \in \grdvar \land v \in \mathbb{Z} \land y \in (\grdvar \cup \constdom) \\
      \absexpr(v, x)  = x' \leq v + 0  & x \in \grdvar \land v \in (\grdvar \cup \constdom) \\
      \absexpr(y + v, x)  = x' \leq y + v & \\
      \grdvar = \grdvar \cup \{y\} & x \in \grdvar \land v \in \mathbb{Z} \land y \notin (\grdvar \cup \constdom)  \\
      \absexpr(\qexpr, x)  = x' \leq 0 + \max(\dbdom) & x \in \grdvar \land \qexpr \text{ is a query expression}  \\
      \absexpr(\bexpr, x) = x' \leq 0 + 1   & x \in \grdvar \land \bexpr \text{ is a boolean expression} \\
      \absexpr(\expr, x) = x' \leq \infty  &  x \in \grdvar \land \expr \text{ doesn't have any of the forms as above} \\
      \absexpr(\expr, x) = \top  &  x \notin \grdvar \\
    \end{array}
    \]
  
  % \wq{ 
    $\grdvar$ is the set of variables used in the guard expression of every while command in the program $c$. 
  % }. 
  In the case 4, if a variable $x$, belonging to the set 
  $\grdvar$ is updated by a variable $y$, which isn't in this set, 
  I add $y$ into the set $\grdvar$ and repeat 
  above procedure  until $\grdvar$ and $\absexpr(\expr, x)$ is stabilized. 
  % \wq{I do not understand this sentence:-(}
  \\
Specifically 
% understanding the intuition, 
we handle a 
% simplified 
normalized guard expression ($ x > 0$ for $x^l \in \lvar_c$)
 in $\ewhile$, and 
%  \wq{I do not understand this sentence:-(}
%  .
% \\
% The counter variables only increase, decrease or reset by expression in the form of arithmetic minus and plus (able to extend to max and min.)
the counter variables only increase, decrease or reset by 
% expression in the form of 
simple arithmetic expression (mainly multiplication, division, minus and plus (able to extend to max and min)). 
This is the same as in paper \cite{sinn2017complexity}. 
\\
For more complex expression assignments, where the counter reset, or calculated from $\elog$, 
multiplication or division, and expressions involving multiple variables, the constraint is approximated as reset of $\infty$.
\\
% This simplification \wq{which part I simplify here?} 
This approximation strategy
doesn't affect our analysis results in our examples. It is easy to extend the normalized expression 
into more complex forms as in \cite{sinn2017complexity}, as well as the 
counter variable manipulation with more advanced expressions.
% \\ 
% The boolean expression in the guard of $\ewhile$ command is normalized into form of $ x > 0$ where $x^l \in \lvar_c$ for some $l$.


\paragraph{Program Event Abstraction}
 I show the abstract event definition, which is generated when computing its abstract execution trace.

\begin{defn}[Abstract Event]
  \label{def:abs_event}
  Abstract Event: 
  $\absevent \in $
  $\ldom \times \dcdom^{\top} \times \ldom$
  is a 
  % pair of abstract initial state and final state.
  triple where the first and third components are labels,
  second component is a constraint from $\dcdom^{\top}$.
  % the thrid % computed from program's abstract final and initial state, $\absfinal(c)$ and $\absinit(c)$ with formal definition, and algorithm detail in Appendix.
  %  the constraint and the third corresponds to a final state.
  \end{defn}
  Specifically, in an abstract event, 
  the first label correspond to an initial state, and 
  the second label and the constraint correspond to an abstract final state.
 The abstract initial state is a label from $\ldom$.
The abstract final state is a pair from $\ldom \times \dcdom^{\top}$,  
where first component is a label from $\ldom$ and the second component is a constraint from $\dcdom^{\top}$.
%

%
Given a program $c$, its abstract initial state,
and the set of its abstract final state is computed as follows,
%
\[
  \begin{array}{ll}
    \absinit(\clabel{\assign{x}{\expr}}{}^l)  & = l  \\
    \absinit(\clabel{\assign{x}{\expr}}{}^l)  & = l \\
    \absinit(\clabel{\eskip}^{l})  & = l \\
    \absinit(\eif [b]^l \ethen c_1 \eelse c_2)  & = l \\
    \absinit(\ewhile [b]^l \edo c)  & = l \\
    \absinit(c_1 ; c_2)  & = \absinit(c_1) \\
 \end{array}
 \]
%
Final State Abstraction: 
$\absfinal: \cdom \to \mathcal{P}(\ldom \times \dcdom^{\top})$,
computes the set of Abstract Final State for the command. 
 \[
  \begin{array}{ll}
    \absfinal(\clabel{\assign{x}{\expr}}{}^l)  & = \{(l, \absexpr\eapp (\expr, x))\}  \\
     \absfinal(\clabel{\assign{x}{\query(\qexpr)}}{}^l)  & = \{
      (l, x' \leq 0 + \max(\dbdom) )\}  \\
     \absfinal(\clabel{\eskip}^{l})  
     & = \{(l, \top)\} \\
     \absfinal(\eif [b]^l \ethen c_1 \eelse c_2)  & = \absfinal(c_1) \cup \absfinal(c_2) \\
     \absfinal(\ewhile [b]^l \edo c)  & = \{(l, \top)\} \\
     \absfinal(c_1 ; c_2)  & =  \absfinal(c_2) \\
 \end{array}
 \]
 %
 \paragraph{Abstract Execution Trace}
 Now, I  extract the abstract execution trace  $\absflow(c)$ for a program, which computes the Abstract Execution Trace for program $c$, as a set of the abstract events $\absevent$.
 %
 \begin{defn}[Abstract Execution Trace]
 \label{def:abs_trace}
  $\absflow \in \cdom \to \mathcal{P}( \ldom \times DC(\mathcal{VAR}  \cup \constdom) \cup \{\top\}) \times \ldom )$
  \end{defn}
 %

 
   I now show how to compute the abstract execution trace. 
  For simplicity, I use $\mathcal{P}(\absevent)$ represent the power set of all abstract events, and I have $\absflow(c) \in \mathcal{P}(\absevent)$.
  I first append a skip command with 
%  a symbolic label $l_e$, i.e., $\clabel{\eskip}^{l_e}$ at the end of the program $c$, and compute the $\absflow(c) = \absflow'(c')$ for $c'$, where $c' = c;\clabel{\eskip}^{l_e}$ as follows,
the exist label $l_{ex}$, i.e., $\clabel{\eskip}^{l_{ex}}$ at the end of the program $c$, 
and compute the $\absflow(c) = \absflow'(c')$ for $c'$, where $c' = c;\clabel{\eskip}^{l_{ex}}$ as follows,
 %
 {\footnotesize
 \[
   \begin{array}{ll}
      \absflow'(\clabel{\assign{x}{\expr}}{}^l)  & = \emptyset  \\
      \absflow'(\clabel{\assign{x}{\query(\qexpr)}}{}^l)  & = \emptyset  \\
      \absflow'([\eskip]^{l})  & = \emptyset \\
      \absflow'(\eif [b]^l \ethen c_t \eelse c_f)  & =  \absflow'(c_t) \cup \absflow'(c_f)
      %   \\ & \quad 
        \cup \{(l, \top,  \absinit(c_t) ) ,  (l, \top, \absinit(c_f)) \} \\
       \absflow'(\ewhile [b]^l \edo c_w)  & =  \absflow'(c_w) \cup \{(l, \top, \absinit(c_w)) \} 
      %  \\ & \quad 
       \cup \{(l', dc, l)| (l', dc) \in \absfinal(c_w) \} \\
       \absflow'(c_1 ; c_2)  & = \absflow'(c_1) \cup  \absflow'(c_2) 
      %  \\ & \quad 
       \cup \{ (l, dc, \absinit(c_2)) | (l, dc) \in \absfinal(c_1) \} \\
   \end{array}
   \]
   }

   Notice $\absflow'([x := \expr]^{l})$, $\absflow'([x := \query(\qexpr)]^{l})$ and $\absflow'([\eskip]^{l})$ are all empty set. 
   For every event $\event$ with label $l$ in an execution trace $\trace$ of program $c$, 
   there is an abstract event in program's abstract execution trace of form $(l, \_, \_)$.  
    I also show the soundness of the abstract execution trace in Appendix.
  %  which says 
  %  \wq{...}
   \begin{lem}[Soundness of the Abstract Execution Trace]
     \label{lem:abscfg_sound}
   Given a program ${c}$, I have:
   %
   \[
     \begin{array}{l}
       \forall \vtrace_0, \trace \in \mathcal{T} ,  \event = (\_, l, \_) \in \eventset \sthat 
   \config{{c}, \trace_0} \to^{*} \config{\eskip, \trace_0 \tracecat \vtrace} 
   \land \event \in \trace 
   \\
   \qquad \implies \exists \absevent = (l, \_, \_) \in (\ldom\times \dcdom^{\top} \times \ldom) \sthat  
   \absevent \in \absflow(c)
   \end{array}
   \]
   \end{lem}
%    This lemma is proved formally in Appendix~\ref{apdx:reachability_soundness}.
% For every event $\event$ with label $l$ in an execution trace $\trace$ of program $c$, 
% there is an abstract event in program's abstract execution trace of form $(l, \_, \_)$. 
This lemma is proved formally in Lemma~\ref{lem:abscfg_sound} in Appendix~\ref{apdx:reachability_soundness}.
\\
For every labeled variable in program $c$, $x^l \in \lvar_c$, there is a unique abstract event in program's abstract execution trace $\absevent \in \absflow(c)$ of form $(l, \_, \_)$. 
\begin{lem}[Uniqueness of the Abstract Execution Trace]
  \label{lem:abscfg_unique}
Given a program ${c}$, I have:
%
\[
  \begin{array}{l}
    \forall \vtrace_0, \trace \in \mathcal{T} ,  \event = (\_, l, \_, \_) \in \eventset^{\asn} \sthat 
\config{{c}, \trace_0} \to^{*} \config{\eskip, \trace_0 \tracecat \vtrace} 
\land \event \in \trace 
\\
\qquad \implies \exists! \absevent = (l, \_, \_) \in (\ldom\times \dcdom^{\top} \times \ldom) \sthat  
\absevent \in \absflow(c)
\end{array}
\]
\end{lem}
This lemma and proof is also 
formalized in Lemma~\ref{lem:absevent_unique} in Appendix~\ref{apdx:reachability_soundness}.

Then, I build the edge for $c$'s abstract control flow graph as follos,
\[
  \absE(c) = \{(l_1, dc, l_2) | (l_1, dc, l_2) \in \absflow(c)\}
  \]

%  I have a pre-processing algorithm to go through the programs and returns the list of labels associating with a loop and whose visiting times need to be analyzed.
%


\paragraph{Abstract Control Flow Graph} 
With the vertices $\absV(c)$ and edges $\absE(c)$ ready, I construct the abstract control flow graph, formally 
% Through a program $c$'s abstract execution trace, its abstract control flow graph is computed 
defined in 
Definition~\ref{def:abs_cfg}.
% Given program $c$ with its abstract control flow $\absflow(c)$, the Abstract Control Flow Graph:
% \\
\begin{defn}[Abstract Control Flow Graph]
\label{def:abs_cfg}
Given a program $c$, 
with its abstract control flow $\absflow(c)$
its abstract control flow graph $\absG(c) =(\absV(c), \absE(c), \absW(c))$ is defined as follows,
\\
% \highlight{
% :
%
% \\
$\absE(c) = \{(l_1, dc, l_2) | (l_1, dc, l_2) \in \absflow(c)\}$,
\\
$\absV(c) = labels(c)\cup\{l_{ex}\}$
\\
 $\absW(c) 
\triangleq \left\{ (l, w) \in \mathbb{L} \times EXPR(\constdom) \right\}$.
% }
% \\
% , where the weight of every label to be computed in the next step.
\end{defn}
% 
% The vertices $\absV(c)$ in this graph are program's labels with an exit label $l_{ex}$.
% Each directed 
%  edge $(l_1, dc, l_2)$ from $l_1$ to $l_2$,
%  represents an abstract transition 
%  between two control locations with a set of difference constraints on it.
% %  , i.e., the labels of two commands (we call the labels also control location and they refer to the same thing), 
% %  where 
% In this transition, the  command labeled with the second location $l_2$, 
%  will be executed after execution of the command with label $l_1$,
% %  The abstract transition contains a set of difference constraints for variables, 
% with the difference constraints generated by abstracting the command of the first label.
% % \\
% % It is easy to show for every $(l_1, dc, l_2) \in \absflow(c)$ such that $l_2 \neq l_e$, $(l_1, l_2) \in flow(c)$. The formal Lemma and proof can be found in Lemma~\ref{lem:flow_to_absflow} in Appendix~\ref{apdx:reachability_soundness}.
Notice I also define the $\absW(c)$ in this graph without giving an actual value.
This $\absW(c)$ is the set of weight for every 
% vertex 
label. The weight is a symbolic expression over the symbolic constant, 
which is the estimated upper bound on the number of visiting time for every control location
through the reachability bound analysis as follows.
%
% It is easy to show for every $(l_1, dc, l_2) \in \absflow(c)$ such that $l_2 \neq l_e$, $(l_1, l_2) \in flow(c)$. The formal Lemma and proof can be found in Lemma~\ref{lem:flow_to_absflow} in Appendix~\ref{apdx:reachability_soundness}.
%
\paragraph*{Abstract Control Flow Graph Through An Example}
%
\input{examples/twoRounds_abscfg}
%
% In order to estimate weight for every vertex in $\progV(c)$,
%  I first show how to compute the reachability bound for every label in $c$
%  % (i.e., every vertex in $\absV(c)$)
%  (i.e., the $\absW(c)$), 
%  then show how to compute the weight for every vertex in $\progV(c)$.
%  \\
%  Through the edges in $\absG(c)$, which correspond to $c$'s abstract transition between labels,

%  \wq{In order to estimate weight for every vertex in the static analysis dependency graph($\progV(c)$), I want to find out the upper bound on 
%  the number of times the labeled command (uniquely associated with a vertex in $\progV(c)$) may be executed when running the program.
%  This information can be obtained by computing the reachability bound for every vertice in the abstract control flow graph ($\absW(c)$), because
%  the vertices in the two graph share the same unique label, the line number.  I can easily show that the reachability bound on one vertex of the actract control flow graph is also the upper bound for the corresponding vertex in the static analysis dependency graph, both vertices share the same unique line number.}



%   I perform the symbolic reachability bound anaysis on the abstract control flow graph, 
%  through the edges in $\absG(c)$, which correspond to $c$'s abstract transition between labels.
%  I infer the invariant for every variable, and compute the transition closure for every abstract transition. By solving the closure
%  with the invariants of variables involved in this closure for every transition, I compute
%  the symbolic reachability bound of every commands corresponding to this transition.
%  \\
%  Specifically in four steps, Variable Modification Tracking, Local Bounds Computation,
%  the symbolic reachability bound of every commands corresponding to this transition. Specifically, this analysis can be performed in four steps:
%   Variable Modification Tracking, Local Bounds Computation,
%  Invariant Inference and Closure Generation, and Reachability Bound Computation,
{In order to estimate weight for every vertex in the static analysis dependency graph($\progV(c)$), I want to find out the upper bound on 
the number of times the labeled command (uniquely associated with a vertex in $\progV(c)$) may be executed when running the program.
This information can be obtained by computing the reachability bound for every vertex in the abstract control flow graph ($\absW(c)$), because
the vertices in the two graph share the same unique label, the line number.  I can easily show that the reachability bound on one vertex of the abstract control flow graph is also the upper bound for the corresponding vertex in the static analysis dependency graph, both vertices share the same unique line number.}


 I perform the symbolic reachability bound analysis on the abstract control flow graph, 
through the edges in $\absG(c)$, which correspond to $c$'s abstract transition between labels.
 I infer the invariant for every variable, and compute the transition closure for every abstract transition. By solving the closure
with the invariants of variables involved in this closure for every transition, I compute
the symbolic reachability bound of every commands corresponding to this transition. Specifically, this analysis can be performed in four steps:
 Variable Modification Tracking, Local Bounds Computation,
Invariant Inference and Closure Generation, and Reachability Bound Computation,
% 
%  I present the details of invariant, closure generation, and reachability bound computation as follows.
with details as follows.
%
%
\paragraph*{Variable Modification Tracking}
Identify the abstract events where each variable is increased, decreased and reset:
\\
$\inc: \mathcal{VAR} \to \mathcal{P}(\absevent) $
the set of the abstract events where the variable increase.
\\
$\inc(x) = \{(\absevent, c) | \absevent = (l, l', x' \leq x + v)\}$
\\
$\reset: \mathcal{VAR} \to \mathcal{P}(\absevent) $
The set of the abstract events where the variable is reset.
\\
$\dec: \mathcal{VAR} \to \mathcal{P}(\absevent) $
The set of abstract events where the variable decrease.
% \\
% $\dec(x) = \{(\absevent, c) | \absevent = (l, l', x' \leq x - v)\}$
\\
$Incr(v) \triangleq \sum\limits_{(\absevent, c) \in \inc(v)}\{\absclr(\absevent) \times v\}$
%
\paragraph*{Local Bounds}
Given a program $c$ with its abstract control flow graph 
$\absG(c) = (\absV, \absE)$
\\
Local Bounds Computation:
$\locbound: \absevent \to \mathcal{VAR} \cup \constdom$.
%
\[ 
\begin{array}{ll}
  \locbound(\absevent) \triangleq 1 
  & \absevent \notin SCC(\absG(c))
  \\
  \locbound(\absevent) \triangleq (x, v) 
  & \absevent \in SCC(\absG(c)) \land \absevent \in \dec(x) \land  \absevent = (\_, \_ , x' \leq x - v) \\
  \locbound(\absevent) \triangleq (x, \max(\dec(x))) 
  & \absevent \in SCC(\absG(c)) \land 
  \absevent  \notin \bigcup_{x \in \mathcal{VAR}} \dec(x)
  \land \absevent \notin SCC(\absG(c) \setminus \dec(x)) 
\end{array}
  \]
  The first case is straightforward. Since variable's visiting time outside of any while loop is at most 1, I do not need to analyze the visiting times of every node in the graph from phase 1.
  The second and third step is guaranteed by the \emph{Discussion on Soundness} in Section 4 of \cite{sinn2017complexity}.
  Then soundness proof is in Lemma~\ref{lem:local_bound_sound} in Appendix~\ref{apdx:reachability_soundness}.
%
\paragraph*{Invariant Inference and Closure Generation }
Then, computing the bound invariants for variables and the transition closures for abstract events:
\\ 
$ \varinvar: \mathcal{VAR} \cup \constdom \to EXPR(\constdom)$
\\
$\absclr: \absevent \to EXPR(\constdom)$
\\
Then, the symbolic invariant for each variable 
as well as the symbolic transition closure for each transition is calculated as follows:
\[ 
\begin{array}{lll}
  \varinvar(x) & \triangleq c & c \in \constdom \\
  \varinvar(x) & \triangleq Incr(v) + \max(\{\varinvar(a) + c | (t, a, c) \in \reset(x)\}) & c \notin \constdom
\end{array}
\]
%
\begin{defn}
  \label{def:transition_closure_base}
\[ 
\begin{array}{lll}
  \absclr(\absevent) 
  & \triangleq x / v & \\ 
  & \locbound(\absevent) = (x, v) \in \constdom \times \mathbb{N} & \\
  \absclr(\absevent) 
  & \triangleq (Incr(x) + 
  \sum\limits_{(\absevent', y, v') \in \reset(x)}
  \absclr(\absevent') \times \max(\varinvar(y) + v', 0) ) / v & \\
  & \locbound(\absevent) = (x, v) \land x \notin \constdom & 
\end{array}
  \]
\end{defn}
%
\paragraph*{Improved Variable Modification Tracking}
Instead of just identifying the abstract events where each variable is reset,
this improvement identifies the chain of the events where a given variable is reset by the 
variables of the abstract events through the chain.
\\
$\resetchain: \mathcal{VAR} \to \mathcal{P}(\mathcal{P}(\absevent)) $
The set of the chain of abstract events where the variable is reset through the chain.
% \\
% $Incr(v) \triangleq \sum\limits_{(\absevent, c) \in \inc(v)}\{\absclr(\absevent) \times v\}$
%
\paragraph*{Improved Invariant Inference and Closure Generation}
Then, computing the bound invariants for variables and the transition closures for abstract events:
\\ 
$ \varinvar: \mathcal{VAR} \cup \constdom \to EXPR(\constdom)$
\\
$\absclr: \absevent \to EXPR(\constdom)$
\\
Then, the symbolic invariant for each variable 
as well as the symbolic transition closure for each transition is calculated as follows:
\[ 
\begin{array}{lll}
  \varinvar(x) & \triangleq c & c \in \constdom \\
  \varinvar(x) & \triangleq Incr(v) + \max(\{\varinvar(a) + c | (t, a, c) \in \reset(x)\}) & c \notin \constdom
\end{array}
\]
%
\begin{defn}
  \label{def:transition_closure}
\[ 
\begin{array}{lll}
  \absclr(\absevent) 
  & \triangleq x / v & \\ 
  & \locbound(\absevent) = (x, v) \in \constdom \times \mathbb{N} & \\
  \absclr(\absevent) 
  & \triangleq \Big(
    \sum\limits_{y \in \{ y ~|~ 
    ch \in \resetchain(x), (l_1, x, y, v, l_2) \in ch \} } Incr(x) & \\
    & \quad + 
  \sum\limits_{ch \in \resetchain(x)}
  \big( \min\limits_{\absevent' \in ch}({\absclr(\absevent')}) \times 
  \max(\varinvar(y) + \sum\limits_{(l_1, x, y, v, l_2) \in ch } v, 0)\big) \Big) / v & \\
  & \locbound(\absevent) = (x, v) \land x \notin \constdom & 
\end{array}
  \]
\end{defn}
  %
% \paragraph*{Adding the Reachability Bounds for Every Vertex in the Data-Control Flow Graph}
% Updating the weight of every vertex in the $\progG(c) = (\progV, \progE, \progW, \progF)$ for program $c$ generated from phase 1. 
% For every $x^l \in \progV$, find the abstract event $\absevent \in \absflow(c)$ of the form $(l, \_, \_)$, updating the $\progW(x^l) $ by the transition closure of this event.
% \\
$
\progW(x^l) 
  \triangleq \absclr(\absevent)
$
\paragraph*{Reachability Bound Computation}
Through the transition closure computed above, 
The weight of every label in 
% Then I update 
the program $c$'s abstract control flow graph,
$\absG(c) =(\absV, \absE, \absW)$
is 
computed as the maximum over all the abstract events $\absevent \in \absE$ heading out from this vertex, formally as follows.
% by annotating each vertex with a symbolic weight. 
% This weight corresponds to 
%reachability bounds of
\\
$\absW 
\triangleq \left\{ (l, w) \in \mathbb{N} \times EXPR(\constdom) | w = \max\limits_{\absevent = (l, \_, \_)} \{ \absclr(\absevent)\} \right\}$.
% \\
\paragraph*{Example}
 I perform the symbolic reachability bound analysis on the abstract control flow graph as follows. 
 I would like to generate the closure of every edge, which is an equality relation between variables.  Solving this closure gives us the reachability bound for this edge. With all the bound for all the edges in the abstract control flow graph, I can calculate the weight for every vertex in this graph. For example, I show the closure generated for the edge 
$(4, j < j - 1, 5)$, 
$\absclr(4, 5) = \varinvar(j)$. The invariant for variable $j$, $\varinvar(j)$ used here is 
$\varinvar(j) = k * \absclr(1, 2)$, which is generated by all the difference constraints involving $j$ in the graph. Notice the $k$ in $\varinvar(j)$ comes from considering both difference constraint $j<=k$ from edge (1,2) and $j<=j-1$ from (4,5), which intuitively reflects the while loop whose counter is set to $k$ at the beginning and decreases by 1 at each iteration. 
With all the closures for all the edges of the abstract control flow graph, I can solve them to obtains the reachability bound of every edge.  I decide the weight for every vertex in the abstract control flow graph by using the bound of the edges which head out from this vertex, by taking the max of the bound from these involving edges. For instance,   
By the constraint on the edge $(4, j \leq j - 1, 5)$, I get bound $k$ for this edge.
Then, I assign vertex $4$ by reachability bound $k$, as in Figure~\ref{fig:abscfg_tworound}(c). 
Another interesting vertex is $2$, which has more than one edge heading out from it, $(2, \top, 3)$ and $(2,\top, 6)$. For the weight for vertex $2$, I choose the max between the bound $k$ from $(2,\top, 3)$ and $1$ from $(2,\top, 6)$.
The same way for the rest weights' computation.
 I use $\absW(c)$ for the set of weights I just computed 
for each label in the abstract control flow graph of $c$.
% Still looking at the two-round example as in Figure~\ref{fig:adapfun_tworound}(b) where 
% each label $l$ is added with a weight by $absW$.
% This weight represents the  maximum reaching times of this location $l$, in the other word, 
% the estimated maximum visiting times of the command labeled with $l$.
% For example, looking at the vertex $1$,
% by analysis steps, since it isn't in any SCC, it's estimated reachability bound is computed as $1$.
% However, for the vertex $4$ which is involved in an SCC, the reachability bound is inferred in another way.
% By the constraint on the edge $4, j \leq j - 1, 5$,
% I first infer its local bound as variable $j$.
% Then by solving the invariant for variable $j$,
% I infer the value bound for $j$, which is $k$.
% Then the reachability bound for this abstract transition, (i.e., edge $4, j \leq j - 1, 5$) 
% is computed as $k$ as well through Definition~\ref{def:abs_trace}.
% In this abstract control flow graph, every vertex is a label,
% corresponding to a label command in the program.
% Each directed 
% edge represents an abstract transition 
% between two control locations, 
% i.e., the labels of two commands (we call the labels also control location and they refer to the same thing), 
% where the second labeled command will be executed after execution of the command with first label.
% For example, the edge $0, a \leq 0, 1$ on the top, represents,
% from location $0$, the command 
% $\clabel{\assign{a}{0}}^0$ is executed with next continuation location $1$,
% where the 
% command $\clabel{\assign{j}{k}}^1$ will be executed next.
% The constraint $a \leq 0$ is generated by abstracting from the assignment command $\assign{a}{0}$,
% representing that value of $a$ is less than or equals to $0$ after 
% location $0$ before executing command at line $1$.
%
The same way for the rest weights' computation.
\paragraph{Vertex Weight Computation}
% The weight for each vertex in $\progV(c)$ is computed as follows,
Then I compute the weight for each vertex in $\progV(c)$,
% as a set of pairs $\progW(c) \in \mathcal{P}(\mathcal{LV} \times \mathcal{LV} \times EXPR(\constdom))$ 
as a set of pairs 
% is the set of pairs 
% The weight for each vertex in $\progV(c)$ is computed 
mapping each $x^l \in \progV(c)$ to a symbolic expression over $\constdom$. Since symbolic expression 
over $\constdom$ is a subset of arithmetic expressions,
we use $\mathcal{A}_{in}$ denotes the arithmetic expression 
over $\mathcal{N}$ and input variable and $\progW(c) \in \mathcal{P}(\mathcal{LV} \times \mathcal{A}_{in})$ 
as follows,
\highlight{
% :
% \\
 \[\progW(c) \triangleq
   \left\{ (x^l, w) 
  %  \in  \mathcal{LV} \times \expr
\mid
x^l \in \progV(c) \land (l, w) \in \absW(c)
\right\}.
\]
}
%
% Since 
 I prove that this 
% symbolic expression is the upper bound for $x^l$'s 
symbolic expression for $x^l \in \progV(c)$ is a sound upper bound of 
the weight for the same vertex $x^l$ in Program's execution-based dependency graph in Appendix~\ref{apdx:reachability_soundness}.
The maximum visiting times of $x^l$ over all execution traces of $c$ in Appendix~\ref{apdx:reachability_soundness}. 
%
\begin{thm}[Soundness of the Reachability Bounds Estimation]
  \label{thm:addweight_soundness}
Given a program ${c}$ with its program-based dependency graph 
$\progG = (\progV, \progE, \progW, \progF)$,
$\traceG = (\traceV, \traceE, \traceW, \traceF)$, I have:
%
\[
\forall (x^l, w_{t}) \in \traceW,
(x^l, w_{p}) \in \progW, \vtrace \in \mathcal{T} \sthat 
% \lvar_c \sthat  
%  \vcounter(\vtrace') l ~ \middle\vert~
% \forall \vtrace \in \mathcal{T} \sthat  
\config{{c}, \trace} \to^{*} \config{\eskip, \trace\tracecat\vtrace'} 
\land 
\config{w_{p}, \trace} \earrow v
\implies
% \right\} 
\leq 
w_{t}(\trace) \leq v
\]
\end{thm}
\paragraph*{Example}
Now let's 
% where I goes 
go back to the Program-Based Dependency Graph which I aim to build for approximating the 
Execution-Based Dependency graph for two-round example, as in
Figure~\ref{fig:twoRounds_example}(c).
%
%  looking at the two-round example,
%  as in  where we
% each vertex in 
%  $l$ is added with a weight by $absW$.
% This weight represents the  maximum reaching times of this location $l$, in the other word, 
% the estimated maximum visiting times of the command labeled with $l$.
% For example, looking at the vertex $1$,
% by analysis steps, since it isn't in any SCC, it's estimated reachability bound is computed as $1$.
% However, for the vertex $4$ which is involved in an SCC, the reachability bound is inferred in another way.
% By the constraint on the edge $4, j \leq j - 1, 5$,
% I first infer its local bound as variable $j$.
% Then by solving the invariant for variable $j$,
Every vertex from $\progV(c)$ in this graph corresponds to a labeled variable, for example $a^5$,
and this label $5$ is also a vertex $5$ in the abstract control flow graph in Figure~\ref{fig:abscfg_tworound}(b).
%
% I infer the value bound for $j$, which is $k$.
% Then the reachability bound for this abstract transition, (i.e., edge $4, j \leq j - 1, 5$) 
Then, it is straight forward, 
that the reachability bound for the label $5$, 
is also the maximum visiting times bound of the labeled variable $a^5$.
% is computed as $k$ as well through Definition~\ref{def:abs_trace}.
% In this abstract control flow graph, every vertex is a label,
% corresponding to a label command in the program.
So, I estimate the visiting time for  labeled variable $a^5$ in Program-Based Dependency Graph in Figrue~\ref{fig:abscfg_tworound}(c) as $k$ as well.
%
The same way for the rest weights' computation.
%
\subsection{Data Dependency Relation Analysis}
\label{sec:alg_edgegen}
% \wq{
   I show how to estimate the directed edges in the static analysis dependency graph.
 I develop a variant of data flow analysis, called Feasible Data-Flow Generation, which 
considers both the control flow and data flow and
is a sound approximation of the edges in the execution based dependency graph.
% }

% \wq{
  Also, worth to mention, I use the result of reaching definition on the abstract control flow graph in feasible 
data-flow generation to have a more precise approximation. Let us see a simple example, a program $ [x = 0]^{1}; [x=2]^{2};  [y = x+1]^{3}$. The standard data flow analysis 
tells us that both the labeled variable $x^{1}$ and $x${2} may flow to $y^{3}$, which will result in an unnecessary edge ($x^{1}, y^{3}$). The result of reaching definition 
can help us eliminate this kind of edge by telling us, at line $3$, only variable $x^{2}$ is reachable. 
% }


% In this step, through 
% % the vertices and edges in 
% $c$'s abstract contrl flow graph $\absG(c)$,
%  $\THESYSTEM$ performs a feasible data-flow analysis 
%  using the reachable definition algorithm,
% %  and then Then I generated the set of feasible data-flow between labeled variables based on that.
% and generates the 
% %set of 
% feasible data-flow relation between labeled variables.
% \\
%  By generating set of all the reachable variables at location of label $l$ in the program $c$.
% For every labelled variable $x^l$ in this set, 
% the value assigned to that variable
% in the assignment command associated to that label is reachable at the entry point of  executing the command of label $l$.
% \\
In the first step, 
it performs the standard reaching definition analysis given a program $c$, 
on 
% its every label $l$
every label in $\absV(c)$.  This step generates set of all the reachable variables at location of label $l$ in the program $c$.
The $\live(l, c)$ represent the analysis result, which is the set of 
reachable labeled variables in program $c$ at the location of label $l$.
For every labelled variable $x^l$ in this set, 
the value assigned to that variable
in the assignment command associated to that label is reachable at the entry point of  executing the command of label $l$.
% \\
% it performs the standard reaching definition analysis given a program $c$, on its every label $l$.
% \\
% Another operator \mathsf{blocks} 
The block, 
is either the command of the form of assignment, skip, or a test of the form of $[b]^{l}$, 
% and $block$ of program $c$ is 
denoted by $\mathsf{blocks}(c)$
the set of all the blocks 
in program $c$, where  $\mathsf{blocks}: \cdom \to \mathcal{P}(\cdom \cup \clabel{\bexpr}^{l})$.
Then it generates the set of feasible data-flow between labeled variables with detail in Definition~\ref{def:feasible_flowsto}, 
based on $\live(l, c)$ for every label in a program $c$ and its blocks $\mathsf{blocks}$.
\\
The details are as follows.
%
% Performing a feasible data-flow analysis through the reachable definition algorithm. 
%  By generating set of all the reachable variables at location of label $l$ in the program $c$.
% For every labelled variable $x^l$ in this set, 
% the value assigned to that variable
% in the assignment command associated to that label is reachable at the entry point of  executing the command of label $l$.
% \paragraph{Generate CFG}
%  \begin{def}
%   \label{def:init_label}
%   Define $\mathsf{init}$: Command -> label, which returns the initial label of the statement. 
% \[
%  \begin{array}{ll}
%     init([x := e]^{l})  & = l  \\
%      init([x := q(e)]^{l})  & = l \\
%      init([skip]^{l})  & = l \\
%      init([if [b]^l then C_1 else C_2]^{l})  & = l \\
%      init([while [b]^l do C]^{l})  & = l \\
%      init(C_1 ; C_2)  & = init(C_1) \\
%  \end{array}
%  \]
% \end{def}
%   Define $\mathsf{final}$: Command -> Powerset(label), which returns the final labels of the statement. 
%  \[
%  \begin{array}{ll}
%     final([x := e]^{l})  & = \{l\}  \\
%      final([x := q(e)]^{l})  & = \{l\}  \\
%      final([skip]^{l})  & = \{l\} \\
%      final([if [b]^l then C_1 else C_2]^{l})  & = final(C_1) \cup final(C_2) \\
%      final([while [b]^l do C]^{l})  & = \{l\} \footnote{while terminates after b evaluates to false} \\
%      final(C_1 ; C_2)  & =  final(C_2) \\
%  \end{array}
%  \]
% \paragraph*{Blocks and Defs}
%  Define block B to be either the command of the form of assignment, skip, or test of the form of $[b]^{l}$.\\
%  Define $\mathsf{blocks}$ : command -> Powerset(Block)
%  \[
%  \begin{array}{ll}
%     blocks([x := e]^{l})  & = \{[x := e]^{l}\}  \\
%      block([x := q(e)]^{l})  & = \{[x := q(e)]^{l}\}  \\
%      blocks([skip]^{l})  & = \{[skip]^{l}\} \\
%      blocks([if [b]^l then C_1 else C_2]^{l})  & = {[b]^{l}} \cup blocks(C_1) \cup blocks(C_2) \\
%      blocks([while [b]^l do C]^{l})  & = \{[b]^{l}\} \cup blocks(C) \\
%      blocks(C_1 ; C_2)  & = blocks(C_1) \cup  blocks(C_2) \\
%  \end{array}
%  \]
%  Define $\mathsf{labels}$ to get the labels of blocks.
%  \[
%    labels(C) = \{l | [B]^{l} \in blocks(C) \}
%  \]  

% The control flow graph is generated by edges between labels. Define $\mathsf{flow}$: command -> P (label $\times$ label ).

% \[
%  \begin{array}{ll}
%     flow([x := e]^{l})  & = \emptyset  \\
%      flow([x := q(e)]^{l})  & = \emptyset  \\
%      flow([skip]^{l})  & = \emptyset \\
%      flow([if [b]^l then C_1 else C_2)  & =  flow(C_1) \cup flow(C_2)\cup \{(l, init(C_1)) , (l, init(C_2)) \} \\
%      flow([while [b]^l do C)  & =  flow(C) \cup \{(l, init(C)) \} \cup \{(l', l)| l' \in final(C) \} \\
%      flow(C_1 ; C_2)  & = flow(C_1) \cup  flow(C_2) \cup \{ (l,init(C_2)) | l \in final(C_1) \} \\
%  \end{array}
%  \]
 
 \paragraph{Reaching definition analysis}
 \todo{extend and formalize}
%  Define block B to be either the command of the form of assignment, skip, or test of the form of $[b]^{l}$.\\
%  Define $\mathsf{blocks}$ : command -> Powerset(Block)
A block  is either the command of the form of assignment, skip, or test of the form of $[b]^{l}$.\\
The operator $\mathsf{blk} : \cdom \to blocks$ gives all the blocks in program $c$.
\\
%  \[
%  \begin{array}{ll}
%     blocks([x := e]^{l})  & = \{[x := e]^{l}\}  \\
%      block([x := q(e)]^{l})  & = \{[x := q(e)]^{l}\}  \\
%      blocks([skip]^{l})  & = \{[skip]^{l}\} \\
%      blocks([if [b]^l then C_1 else C_2]^{l})  & = {[b]^{l}} \cup blocks(C_1) \cup blocks(C_2) \\
%      blocks([while [b]^l do C]^{l})  & = \{[b]^{l}\} \cup blocks(C) \\
%      blocks(C_1 ; C_2)  & = blocks(C_1) \cup  blocks(C_2) \\
%  \end{array}
%  \]
 Set $?$ to be undefined:
 \\
%  $label^{?}$ is label $\cup \{?\}$.\\
%  Define $\mathsf{kill}$: $blocks \to \mathcal{P}(\mathcal{VAR} \times LABEL \cup \{?\})$, which produces the set of labelled variables of assignment destroyed by the block.
The operator $\mathsf{kill}$: $blocks \to \mathcal{P}(\mathcal{VAR} \times \ldom \cup \{?\})$ produces the set of labelled variables of assignment destroyed by the block.
 \\
  % Define $\mathsf{gen}$: $blocks \to \mathcal{P}(\mathcal{VAR} \times LABEL \cup \{?\})$, which generates the set of labelled variables generated by the block.
  The operator $\mathsf{gen}$: $blocks \to \mathcal{P}(\mathcal{VAR} \times \ldom \cup \{?\})$ generates the set of labelled variables generated by the block.
  \\
  % Define $defs(x)(c): \mathcal{VAR} \to LABEL$, gives all the labels where assigns value to variable x in the target program $c$. 
  % The operator  $defs(c): \mathcal{VAR} \to \ldom$ gives all the labels where assigns value to variable in $c$. 
%  \[
%  \begin{array}{ll}
%     kill([x := e]^{l})  & = \{ (x, ?) \} \cup \{ (x, l') | l' \in defs(x) \} \\
%      kill([x := q(e)]^{l})  & = \{ (x, ?) \} \cup \{ (x, l') | l' \in defs(x) \}  \\
%      kill([skip]^{l})  & = \emptyset \\
%      kill([ [b]^l ]^{l})  & =  \emptyset
%  \end{array}
%  ~~
%   \begin{array}{ll}
%       gen([x := e]^{l})  & = \{ (x, l) \}  \\
%      gen([x := q(e)]^{l})  & = \{ (x, l) \}  \\
%      gen([skip]^{l})  & = \emptyset \\
%      gen([ [b]^l ]^{l})  & =  \emptyset 
%  \end{array}
%  \]
%  Define $in(l)$, $out(l)$: LABEL$ \to \mathcal{VAR} \times LABEL \cup \{?\}$ for every block in program $c$ is computed as follows,
%  \[
%  \begin{array}{lll}
%     in(l)  & = \{ (x, ?) | x^l \in \lvar_c \land  l = \absinit(c) \}  
%     \cup \{ out(l')|  | (l',\_, l) \in \absE \land  l \neq \absinit(c)\}  \\
%      out(l)  & =  gen(B^{l}) \cup \{ in(l) \setminus kill(B^l)  \} & B^l \in blocks(c)   
%  \end{array}
%  \]
%  computing $in(l)$ and $out(l)$ for every $B^l \in blocks(c) $, and repeating these two step
% until the $in(l)$ and $out(l)$ are stabilized for every $B^l \in blocks(c) $
%  I use $\live_{in}(l,c)$ and $\live_{out}(l, c)$ denote the stabilized results for the command of label $l$ in program $c$. 
%  Define $defs(x)(c): \mathcal{VAR} \to LABEL$, gives all the labels where assigns value to variable x in the target program $c$.
% Define $defs(x)(c): \mathcal{VAR} \to \ldom$, gives all the labels where assigns value to variable x in the target program $c$.
% \\
%  Define $in(l)$, $out(l)$: $ \ldom \to \mathcal{VAR} \times LABEL \cup \{?\}$ for every block in program $c$ is computed as follows,
The operator  $in(l)$, $out(l)$: $ \ldom \to \mathcal{LV} \cup \{?\}$ for every block in program $c$ is defined as follows,
 \[
 \begin{array}{ll}
    % in(l)  & = \{ (x, ?) | x^l \in \lvar_c \land  l = \absinit(c) \}  
    in(l)  & = \{ x^{?} | x^l \in \lvar_c \land  l = \absinit(c) \}  
    \cup \{ out(l')|  | (l',\_, l) \in \absE(c) \land  l \neq \absinit(c)\}  \\
     out(l)  & =  gen(B^{l}) \cup \{ in(l) \setminus kill(B^l)  \}  
 \end{array}
 \]
computing $in(l)$ and $out(l)$ for every $B^l \in blocks(c) $, and repeating these two steps
until the $in(l)$ and $out(l)$ are stabilized for every $B^l \in blocks(c) $
%  I use $\live_{in}(l,c)$ and $\live_{out}(l, c)$ denote the stabilized results for the command of label $l$ in program $c$. 
 I use $\live(l,c)$ to represent 
% $\live_{in}(l,c)$ in the other part of the paper.
denote the stabilized result of $in(l)$ at label $l$ in program $c$. 
% The $\live_{in}(l,c)$ and $\live_{out}(l, c)$ is computed by the Standard worklist algorithm. (For simplicity, I use $\live(l,c)$ to represent $\live_{in}(l,c)$ in the other part of the paper.}
\\
% The $\live_{in}(l,c)$ and $\live_{out}(l, c)$ 
The stabilized $in(l)$ and $out(l)$ for program $c$, as well as $\live(l, c)$,
is computed by the standard worklist algorithm with detail as below. 
% For simplicity, I use $\live(l,c)$ to represent $\live_{in}(l,c)$ in the other part of the paper.
\begin{enumerate}
    \item initial in[l]=out[l]=$\emptyset$
    \item initial in[entry label] = $\emptyset$
    \item initialize a work queue, contains all the blocks in C
    \item while |W| != 0 \\
         pop l in W\\
          old = out[l]\\
          in(l) =  out(l') where $(l',\_, l) \in \absE(c)$\\
           out(l) = gen($b^l$) $\cup$ (in(l) - kill($b^l$) ) where $b^l$ in $\mathsf{blk}(c)$   \\
          if (old != out(l)) W= W $\cup$ \{l'| (l,l') in $(l',\_, l) \in \absE(c)$\}\\
          end while
\end{enumerate}
%
% computing $in(l)$ and $out(l)$ for every $B^l \in blocks(c) $, and repeating these two step
% until the $in(l)$ and $out(l)$ are stabilized for every $B^l \in blocks(c) $
%  I use $\live_{in}(l,c)$ and $\live_{out}(l, c)$ denote the stabilized results for the command of label $l$ in program $c$. 
% The $\live_{in}(l,c)$ and $\live_{out}(l, c)$ is computed by the Standard worklist algorithm. (For simplicity, I use $\live(l,c)$ to represent $\live_{in}(l,c)$ in the other part of the paper.
%%
\paragraph{Feasible Data-Flow Generation}
by using the results of Reaching definition analysis results, specifically $\live(l, c)$ for every label in a program $c$, I refine the vertices and edges in the $\absG$ graph 
by generating the set of feasible data-flow between labeled variables as follows,
%
%   \[
%  \begin{array}{ll}
%     dcdg([x := e]^{l})  & = \{ (y^i, x^l) | y \in VAR(e) \land (y,i) \in \live_{in}(l) \}  \\
%      dcdg([x := q(e)]^{l})  & = \{ (y^i, x^l) | y \in VAR(e) \land (y,i) \in \live_{in}(l) \}  \\
%      dcdg([skip]^{l})  & = \emptyset \\
%      dcdg([if [b]^l then C_1 else C_2)  & =  dcdg(c_1) \cup dcdg(c_2)\\ & \cup \{(x^i,y^j) | x \in VAR(b) \land (x,i) \in \live_{in}(l) \land ([y = \_]^j) \in blocks(c_1) \} \\
%      &\cup \{(x^i,y^j) | x \in VAR(b) \land (x,i) \in \live_{in}(l) \land ([y = \_]^j) \in blocks(c_2) \} \\
%      dcdg([while [b]^l do c)  & =  dcdg(c) \cup \{(x^i,y^j) | x \in VAR(b) \land (x,i) \in \live_{in}(l) \land ([y = \_]^j) \in blocks(C) \} \\
%      dcdg(c_1 ;c_2)  & = dcdg(c_1) \cup  dcdg(c_2) \\
%  \end{array}
%  \]
%
\begin{defn}[Feasible Data-Flow]
  \label{def:feasible_flowsto}
  Given a program $c$ and two labeled variables $x^i, y^j$  in this program, 
  $\flowsto(x^i, y^j, c)$ is 
    {\footnotesize
    \[
   \begin{array}{ll}
    \flowsto(x^i, y^j, \clabel{\assign{x}{\expr}}{}^l)  & \triangleq (x^i, y^j) \in \{ (y^i, x^l) | y \in \mathsf{FV}(\expr) 
    % \land (y,i) \in \live(l, \clabel{\assign{x}{\expr}}^l) \}  \\
    \land y^i \in \live(l, \clabel{\assign{x}{\expr}}^l) \}  \\
    \flowsto(x^i, y^j, \clabel{\assign{x}{\query(\qexpr)}}{}^l)  & \triangleq (x^i, y^j) \in \{ (y^i, x^l) | y \in \mathsf{FV}(\qexpr) 
    % \land (y,i) \in \live(l,\clabel{\assign{x}{\query(\qexpr)}}^l) \}  \\
    \land y^i \in \live(l,\clabel{\assign{x}{\query(\qexpr)}}^l) \}  \\
    \flowsto(x^i, y^j, [\eskip]^{l})  & = \emptyset \\
    \flowsto(x^i, y^j, \eif ([b]^l, c_1, c_2))  & \triangleq \flowsto(x^i, y^j, c_1) \lor \flowsto(x^i, y^j, c_2) \\ 
        & \lor (x^i, y^j) \in
       \{(x^i,y^j) | x \in \mathsf{FV}(b) \land 
      %  (x,i) 
      x^i \in \live(l, \eif ([b]^l, c_1, c_2)) \land  y^j \in \lvar(c_1) \\
    %   ([y = \_]^j) \in \mathsf{blk}(c_1) \} \\
       &\lor (x^i, y^j) \in \{(x^i,y^j) | x \in \mathsf{FV}(b) \land 
      %  (x,i) 
      x^i\in \live(l, \eif ([b]^l, c_1, c_2))  \land  y^j \in \lvar(c_2) \\
    %   \land ([y = \_]^j) \in \mathsf{blk}(c_2) \} \\
       \flowsto(x^i, y^j, \ewhile [b]^l \edo c_w)  & \triangleq  \flowsto(x^i, y^j, c_w)  \lor
       \\ & 
       (x^i, y^j) \in  \{(x^i,y^j) | x \in \mathsf{FV}(b) \land 
      %  (x,i) 
      x^i \in \live(l,   \ewhile [b]^l \edo c_w) \land  y^j \in \lvar(c_w) \\
    %   ([y = \_]^j) \in \mathsf{blk}(c_w) \} \\
       \flowsto(x^i, y^j, c_1 ;c_2)  & \triangleq \flowsto(x^i, y^j, c_1) \lor \flowsto(x^i, y^j, c_2) \\
   \end{array}
   \]
   }
   \end{defn}
%
This \emph{Feasible Data-Flow} relation is a sound approximation 
of the \emph{variable may-Dependency} relation over labeled variables for every program.
The soundness is proved
in Appendix~\ref{apdx:flowsto_soundness}.
%
\paragraph*{Edges Estimation}
Then I define the estimated directed edges
% for each vertex in $\progV(c)$,
between vertices in $\progV(c)$,
as a set of pairs 
% $\progW(c) \in \mathcal{P}(\mathcal{LV} \times \mathcal{LV} \times EXPR(\constdom))$ 
$\progE(c) \in \mathcal{P}(\in \mathcal{LV} \times \mathcal{LV})$
% is the set of pairs 
% The weight for each vertex in $\progV(c)$ is computed 
indicating a directed edge from the first vertex to the second one in each pair
as follows,
\highlight{
  \[
    \progE(c) \triangleq 
    \left\{ 
    ({x}_1^{i}, {x}_2^{j}) \in \mathcal{LV} \times \mathcal{LV}
    ~ \middle\vert ~
    \begin{array}{l}
      {x}_1^{i}, {x}_2^{j} \in \progV(c)
    \land
      % \\
      \exists n \in \mathbb{N}, z_1^{r_1}, \cdots, z_n^{r_n} \in \lvar_{{c}} \sthat  
      n \geq 0 \land
      \\
      \flowsto(x^i,  z_1^{r_1}, c) 
      \land \cdots \land \flowsto(z_n^{r_n}, y^j, c) 
    \end{array}
    \right\}
    \]
}
This estimated directed edge set $\progE(c)$ is a sound approximation of the 
edge set in $c$'s execution-based dependency graph, which is proved 
in Appendix~\ref{apdx:adapt_soundness}.
%  \begin{defn}[Feasible Data-Flow]
%   \label{def:feasible_flowsto}
%     {\footnotesize
%     \[
%    \begin{array}{ll}
%       dcdg(\clabel{\assign{x}{\expr}}{}^l)  & = \{ (y^i, x^l) | y \in FV(e) \land (y,i) \in \live_{in}(l, \clabel{\assign{x}{\expr}}^l) \}  \\
%        dcdg(\clabel{\assign{x}{\query(\qexpr)}}{}^l)  & = \{ (y^i, x^l) | y \in FV(e) \land (y,i) \in \live_{in}(l,\clabel{\assign{x}{\query(\qexpr)}}^l) \}  \\
%        dcdg([\eskip]^{l})  & = \emptyset \\
%        dcdg([\eif [b]^l \ethen c_1 \eelse c_2)  & =  dcdg(c_1) \cup dcdg(c_2)\\ & \cup 
%        \{(x^i,y^j) | x \in FV(b) \land (x,i) \in \live_{in}(l) \land ([y = \_]^j) \in blocks(c_1) \} \\
%        &\cup \{(x^i,y^j) | x \in FV(b) \land (x,i) \in \live_{in}(l) \land ([y = \_]^j) \in blocks(c_2) \} \\
%        dcdg([\ewhile [b]^l \edo c)  & =  dcdg(c) \cup \{(x^i,y^j) | x \in FV(b) \land (x,i) \in \live_{in}(l) \land ([y = \_]^j) \in blocks(C) \} \\
%        dcdg(c_1 ;c_2)  & = dcdg(c_1) \cup  dcdg(c_2) \\
%    \end{array}
%    \]
%    }
%    \end{defn}
%    For any two labeled variables $x^i, y^j$ in a program $c$, 
%   %  it is easy to see that there is a one-on-one correspondence between 
%   %  $\flowsto$ relation of the two variables, and the $dcdg$ analysis result on $c$.
%   I use $\flowsto()$ denote if they have a feasible data-flow relation in Definition~\ref{def:flowsto}.
%    \begin{defn}[Feasible Data-Flow ($\flowsto$)]
%    \label{def:flowsto}
%    \[
%    \forall c \in \cdom, x^i, y^j \in \lvar_c \sthat  
%    \flowsto(x^i, y^j, c) \iff (x^i, y^j) \in dcdg(c)
%    \]
%    \end{defn}
  %  This soundness is proved in Proof~\ref{pf:rd_soundness} in Appendix~\ref{apdx:rd_soundness}.
  %  For any two labeled variables in a program $c$, it is easy to see that there is a one-on-one correspondence between 
  %  $\flowsto$ relation of the two variables, and the $dcdg$ analysis result on $c$.
  %  \begin{thm}[Soundness of the Feasible Data-Flow Analysis]
  %  \label{thm:rd_soundness}
  %  \[
  %  \forall c \in \cdom, x^i, y^j \in \lvar_c \sthat  
  %  \flowsto(x^i, y^j, c) \iff (x^i, y^j) \in dcdg(c)
  %  \]
  %  \end{thm}
  %  This soundness is proved in Proof~\ref{pf:rd_soundness} in Appendix~\ref{apdx:rd_soundness}.
  \paragraph*{Example}
% Still looking at the Figure~\ref{fig:adapfun_tworound}(c), 
% and taking the edge $(l^6, a^5)$ for example.
% By $\flowsto(l^6, a^5, c)$, I can see $a$ is used directly in the query expression $\chi[k]*a$,
% in the assignment command $\clabel{\assign{l}{\query(\chi[k]*a)}}^l$,
% i.e., $a \in FV(\chi[k]*a)$.
% Also, from the Reaching definition analysis, I know $a^5 \in \live(6, two-round)$.
% Then I have $\flowsto(l^6, a^5, c)$ and construct the edge $(l^6, a^5)$.
% And same way for constructing the rest edges.
%
The edge $(l^6, a^5)$ in Figure~\ref{fig:twoRounds_example}(c) is constructed by this definition.
% and take  for example.
By $\flowsto(l^6, a^5, c)$, I can see $a$ is used directly in the query expression $\chi[k]*a$,
in the assignment command $\clabel{\assign{l}{\query(\chi[k]*a)}}^l$,
i.e., $a \in FV(\chi[k]*a)$.
Also, from the reaching definition analysis, I know $a^5 \in \live(6, \kw{twoRounds(k)})$.
Then I have $\flowsto(l^6, a^5, c)$ and construct the edge $(l^6, a^5)$.
And the same way for constructing the rest edges. Also, the edge $(x^3,j^5)$ in the same graph represents the control flow, 
caught by the $\flowsto$ relation.

% Still looking at the Figure~3(c) in main paper, 
% and taking the edge $(l^6, a^5)$ for example.
% By $\flowsto(l^6, a^5, c)$, I can see $a$ is used directly in the query expression $\chi[k]*a$,
% in the assignment command $\clabel{\assign{l}{\query(\chi[k]*a)}}^l$,
% i.e., $a \in FV(\chi[k]*a)$.
% Also, from the Reaching definition analysis, I know $a^5 \in \live(6, two-round)$.
% Then I have $\flowsto(l^6, a^5, c)$ and construct the edge $(l^6, a^5)$.
% And same way for constructing the rest edges. Also, the edge $(x^3,j^5)$ in the same graph represents the control flow, caught by our $\flowsto$ relation.
%
