\paragraph*{Chapter Outline}
This chapter includes following parts. 
\begin{enumerate}
   \item Previous Works on Adaptive Data Analysis in Section~\ref{sec:prework}.
   \item A new program analysis framework for the adaptivity of Adaptive Data Analysis in Chapter~\ref{sec:adapt-analysis}.
   This program analysis framework has three major components,
   \begin{enumerate}
      \item A while-like language extended with query request feature, named {\tt Query While} Language, 
      used to implement the adaptive data analysis in Section~\ref{sec:adapt-language}. 
      \item A formal adaptivity model through execution-based adaptivity analysis in Section~\ref{sec:adapt-exe}.
      \item A static program analysis algorithm, named {\THESYSTEM} through static adaptivity analysis in Section~\ref{sec:adapt-static}.
   \end{enumerate}
   \item The manual examples demonstrating the new adaptivity analysis framework, and the evaluation results from the implementation
   of this analysis framework in Section~\ref{sec:adapt-implementation}.
   \item Section~\ref{sec:adapt-relatedwork} presents the related works in the program analysis and the data analysis areas
   related to our adaptivity analysis framework.
\end{enumerate}


\paragraph{Contributions}
This chapter has the following contributions.
\begin{enumerate}
   \item A new programming framework for adaptive data analyses
   where the program represents an analyst that can query a generalization-preserving mechanism mediating the access to some data. 
   This programming framework can support more general data analysis programs than existing adaptivity analysis works.
   %  is extended from existing framework,  with inputs and inter-procedure call.
   % \item A trace-based operational semantics for the loop language, specific to dependency between queries.
   \item 
   % {A formal definition of the notion of adaptivity under the analyst-mechanism model. This definition is built on a query-based dependency graph built out of all the possible program execution traces.}
   A new formal definition of the notion of adaptivity under the analyst-mechanism model. 
   This definition is built on a variable-based dependency graph that is constructed using sets of program execution traces.
   This definition formalizes the intuitive \emph{adaptivity} more precise than previous adaptivity formalization.
   % \item A transformation between the {\tt Loop} language and the ssa language, with the soundness of the transformation.
   \item 
   % A program analysis algorithm {\THESYSTEM} which provides an upper bound on the adaptivity via a variable-based dependency graph.
   A new static program analysis algorithm {\THESYSTEM} combining data flow,
   control flow and reachability bound analysis in order to provide tighter bounds on the adaptivity of a program than previous works.
   %
   \item A soundness proof of the program analysis showing that the adaptivity estimated by {\THESYSTEM} bounds the true adaptivity
   (i.e., the \emph{adaptivity} formalized for the program through the execution-based analysis) of the program. 
   \item An implementation of {\THESYSTEM} and an experimental evaluation the bounds this implementation provides on several examples.
   % \item A path-sensitive program reachability bound analysis algorithm designed for program with application beyond adaptivity analysis
   %  with implementation.
   % \item An accurate full-spectrum program resource cost analysis, 
   % generalized from {\THESYSTEM} with implementation.
\end{enumerate}
%
% \todo{combine}
% \paragraph*{Contributions and Improvements}
% Given the limitation of existing reachability bound analysis techniques, I designed a path-sensitive reachability bound 
% analysis algorithm

% Based on the implementation and experimental results of the basic full-spectrum analysis,
% % $\THESYSTEM$,
% I 
% % also focus on the two further features can be 
% extend it in Section~\ref{ch:improved} in following 3 aspects.
% % \begin{enumerate}
% %  \item The precision of formalizing the intuitive \emph{adaptivity} 
% % %  in the formal  model 
% % through the execution-based program analysis.

% % \item In static program analysis, I will give a tighter estimated upper bound on dependency quantity through 
% % path sensitive reachability bound analysis techniques. 

% % % \item In the third step of static program analysis, I will improve the accuracy of the adaptivity computation algorithm,
% % % compute a tighter adaptivity upper bound as well.
% % \end{enumerate}
% \begin{enumerate}
%    \item The {\tt Query While} Language is extended in Section~\ref{sec:refine-exe-language} with inter-procedure call.
%    \item In the execution-based \emph{adaptivity} analysis part,
%    the precision of formalizing the intuitive \emph{adaptivity} is improved, with extension on the
% %  in the formal  model 
% % in the meantime extend this analysis with 
% inter-procedure call in Section~\ref{sec:refine-exe}.
% \item The static program \emph{adaptivity} analysis is extended inter-procedure call as well, 
% and improved by
% giving a tighter estimated upper bound on \emph{adaptivity} in Section~\ref{sec:refine-static}.
% %  give a tighter estimated upper bound 
% Especially in order to improve the accuracy of the estimated result, a
% % I improve the accuracy of the static \emph{dependency quantity} analysis in the second step through 
% % designing a
% path sensitive reachability bound analysis algorithm is designed in Section~\ref{sec:refine-static-psreachability}.
% Based on this newly designed algorithm,
% I improve the accuracy of the static \emph{dependency quantity} analysis in the second step 
% is improved, and a tighter upper bound on \emph{adaptivity} is computed correspondingly.
% % \item In the third step of static program analysis, I will improve the accuracy of the adaptivity computation algorithm,
% % compute a tighter adaptivity upper bound as well.
% \end{enumerate}

%%%%% To reason about%
