The previous works on formalizing the adaptivity is through a query-based dependency graph.
Below is a summary of their query-based dependency graph construction and adaptivity formal definition, followed
by the weaknesses of this formalization method.
\subsection*{Query-Based Dependency Graph}
Below is the formal definition of query may dependency based on their trace-based operational semantics from \todo{Thesis}.
The notations $\in_q$ and $\not\in_q$ a query belongs to the trace or not repectively, with the formal definition in \todo{Thesis}.

\begin{defn}[Query may dependency]
One query $q({v_q}_1)$ may depend on another query $q({v_q}_2)$ in a program $c$, with a starting loop maps $w$, a starting memory $m$, hidden database $D$, denoted as \\
$\mathsf{DEP}(q({v_q}_1)^{(l_1, w_1)}, q({v_q}_2)^{(l_2, w_2)}, c,w, m, D)$ is defined below. 
\[
\begin{array}{l}
\forall  t. \exists m_1,m_3,t_1,t_3,c_2.\\
  \left (\begin{array}{l}   
\config{m, c,  t,w} \rightarrow^{*} \config{m_1, [\assign{x}{q({v_q}_1)}]^{l_1} ; c_2,
  t_1,w_1} \rightarrow \\ \config{m_1[q({v_q}_1)(D)/x], c_2,
  t_1++[q({v_q}_1)^{(l_1, w_1)}], w_1} \rightarrow^{*} \config{m_3, \eskip,
  t_3,w_3} \\  
  \land \\
\Big( q({v_q}_1)^{(l_1,w_1)} \in_{q} (t_3-t) \land q({v_q}_2)^{(l_2,w_2)} \in_{q} (t_3-t_1) \\ \implies  \exists v \in \codom(q({v_q}_1)), m_3', t_3', w_3'.  \\
 \config{m_1[v/x], {c_2}, t_1++[q({v_q}_1)^{(l_1,w_1)}], w_1} \rightarrow^{*} \config{m_3', \eskip, t_3', w_3'} \\ \land (q({v_q}_2)^{(l_2,w_2)}) \not \in_{q} (t_3'-t_1)
\Big)\\
\land \\
\Big(q({v_q}_1)^{(l_1,w_1)} \in_{q} (t_3-t) \land q({v_q}_2)^{(l_2,w_2)} \not\in_{q} (t_3-t_1) \\ \implies  \exists v \in \codom(q({v_q}_1)),  m_3', t_3', w_3'. \\
 \config{m_1[v/x], {c_2}, t_1++[q({v_q}_1)^{(l_1,w_1)}], w_1} \rightarrow^{*} \config{m_3', \eskip, t_3', w_3'} \\ \land (q({v_q}_2)^{(l_2,w_2)})  \in_{q} (t_3'-t_1)
\Big)
\end{array} \right )
\end{array}
\]
\end{defn}
%
Based on the \emph{may-dependency} between the two queries above,
below is their formal definition of query-based dependency graph. 
For every execution of a program $c$ staring with different configurations, 
they construct a corresponding dependency graph.  
% graph definition
\begin{defn}[Query-based Dependency Graph]
Given a program $c$, a database $D$, a starting memory $m$, an initial loop map $w$, the query-based dependency graph $G(c,D,m,w) = (V, E)$ is defined as: \\
$V =\{q({v_q})^{l,w} \in \mathcal{AQ} \mid \forall t. \exists m',  w', t'.  \config{m ,c, t, w}  \to^{*}  \config{m' , \eskip, t', w' }  \land q({v_q})^{l,w} \in {(t'-t)}  \}$.
\\
$E = \left\{(q({v_q})^{(l,w)},q({v_q}')^{(l',w')}) \in \mathcal{AQ} \times \mathcal{AQ} 
~ \left \vert ~ \mathsf{DEP}(q({v_q}')^{(l',w')},q({v_q})^{(l,w)}, c,w,m,D)
 \right.\right\}$.
\end{defn}
%
% The function $\mathsf{To}(q(v')^{(l',w')}, q(v)^{(l,w)}$ tells that the query request $q(v')^{(l',w')}$ appears after the query request $q(v)^{(l,w)}$ in the trace, by comparing the annotation $(l',w')$ and $(l,w)$. It helps to decide on the direction of one edge.
The edge is directed, when an annotated query $q({v_q})^{(l,w)}$ may depend on its previous query $q({v_q}')^{(l',w')}$, we have the directed
edge $(q({v_q})^{(l,w)}, q({v_q}')^{(l'.w')})$, from $q({v_q})^{(l,w)} $ to $q({v_q}')^{(l'.w')}$.

The query-based dependency graph only considers the newly generated annotated queries during the execution of the program $c$,
so we see the nodes coming from the trace $t'-t$.
The previous trace before the execution of $c$ is excluded when constructing the graph.
% To summarize, for every execution of a program $c$ staring with different configurations, 
% they can construct a corresponding dependency graph. 

\subsection*{Adaptivity Formalization}
Below is the definition of adaptivity from \todo{Thesis}, by means of the query-based dependency graph. 
\begin{defn}[Adaptivity in {loop} language]
Given a program $c$, and a memory $m$, a database $D$, a starting loop map $w$, the adaptivity of the dependency graph $G(c, D,m,w) = (V, E)$ is the length of the longest path in this graph. We denote the path from $q({v_q})^{(l,w)}$ to $q({v_q}')^{(l',w')}$ as $p(q({v_q})^{(l,w)}, q({v_q}')^{(l',w')} )$. The adaptivity denoted as $A(c, D, m, w)$.
%
$$A(c, D, m, w) = \max\limits_{q({v_q})^{(l,w)},q({v_q}')^{(l',w')} \in V } |p(q({v_q})^{(l,w)}, q({v_q}')^{(l',w')} )| $$
\end{defn}
\subsection*{Limitations}
Limited by their language design and the dependency graph construction,
this adaptivity definition is weak in the following senses.
\begin{itemize}
    \item \textbf{Expressiveness Limitation}
    \\
    The definition isn't general enough to give the formal adaptivity for the adaptive data analysis programs with non-constant
    while loops. However, while loops with non-deterministic number of iterations are common in adaptive data analysis programs.
    \item \textbf{Accuracy Limitation}
    \\
    This definition relies on a specific memory, while map, and an execution trace.
    It gives the adaptivity for the adaptive data analysis program w.r.t. one specific
    execution. In the other words, this value isn't indeed the adaptivity for the program, but for the program under one single execution.
    % to The trace only tracks the query requests. This lost the information of the variables
    % which are assigned by query values even they are not assigned by query requests. 
    \item \textbf{Efficiency Limitation}
    \\
    This definition is in-efficient in the senses that it requires the fully unfolding of every iteration of the while loop.
    There are two reasons for this low-Efficiency.
    The first one comes from the low-efficiency of their trace-based operational semantics,
    which requires the trace to track the loop iteration number in the annotated query.
    The other is caused by their dependency graph generation, which requires every query requests evaluated during the program execution
    as the graph nodes.
    Both of the two processes generate unnecessary and duplicate nodes during the while iterations.
    %  annotatation of the  the query request executed in the program
    % with integer indicating the while loops. 
\end{itemize}