\section*{Acknowledgments}

I would like to first express my sincerest thanks to Boston University, it is a great experience to study, do research, and enjoy my life here. I am so lucky that I made my decision to transfer to Boston University during the summer of 2019. I like the seminars, like the classes, like my colleagues here, like the discussion about logic, type systems. 

I have been at BU for more than two years. Before that, I stayed at Buffalo for three years. Reviewing my path to Ph.D., so many people have helped me. In particular, I would like to say thank you so much to my advisor, Professor Marco Gaboardi. Thanks for your being an amazing advisor, for your bringing me to BU, for encouraging me to attend conferences, for providing great opportunities to collaborate with great researchers, for teaching me how to become a better human being! I am so fortunate that I can work with Marco for these years.

I want to thank my committee members. Great thanks to Professor Assaf Kfoury for your kindness in being the chair of my committee, and Professor Hongwei Xi for being the committee member of my dissertation. I want to thank Professor Alley Stoughton for your patience to read my dissertations so carefully and all your suggestions are important in this dissertation. I learned a lot from you, especially in Easycrypt. I also want to thank Deepak, for your kindness to be my committee member even though you are in Germany, for your invitation to MPI-SWS during the summers of 2018 and 2019, for your great ideas on the works presented in this dissertation, and for your careful reading and suggestions on improving this dissertation!

I would like to thank all my colleagues at Boston University as well as at the University at Buffalo. Thanks to Professor Lukasz Ziarek for his help at Buffalo. Thanks to all my collaborators in these works in the dissertation.

Last, but by no means least, I want to thank my father, Peijun Qu, my mother, Hui Jin, for your support in pursuing my Ph.D. I am also thankful to my family members, my grandfather Xiaoping Qu, grandmother Ling Zhang. Thanks to my loving Liuyi Yao, lovely cats Cream, Oreo, Ergou, Nainiu, Haowen for their company. 

