The previous works on formalizing the adaptivity is through a query-based dependency graph.
Below is a summary of their query-based dependency graph construction and adaptivity formal definition, followed
by the weaknesses of this formalization method.
\subsection*{Query-Based Dependency Graph}
They build their dependency graph over annotated queries, in order to construct the edge between queries for this graph, they first
define a query \emph{May-Dependency} relation. Below is a summary of this definition from
% Below is the formal definition of query may dependency based on their trace-based operational semantics 
from Thesis~\cite{weihao22}.
The notations $\in_q$ and $\not\in_q$ a query belongs to the trace or not respectively, with the full details in Thesis~\cite{weihao22}.
\begin{defn}[Query may dependency]
One query $q({v_q}_1)$ may depend on another query $q({v_q}_2)$ in a program $c$, with a starting loop maps $w$, a starting memory $m$, hidden database $D$, denoted as \\
$\mathsf{DEP}(q({v_q}_1)^{(l_1, w_1)}, q({v_q}_2)^{(l_2, w_2)}, c,w, m, D)$ is defined below. 
\[
\begin{array}{l}
\forall  t. \exists m_1,m_3,t_1,t_3,c_2.\\
  \left (\begin{array}{l}   
\config{m, c,  t,w} \rightarrow^{*} \config{m_1, [\assign{x}{q({v_q}_1)}]^{l_1} ; c_2,
  t_1,w_1} \rightarrow \\ \config{m_1[q({v_q}_1)(D)/x], c_2,
  t_1++[q({v_q}_1)^{(l_1, w_1)}], w_1} \rightarrow^{*} \config{m_3, \eskip,
  t_3,w_3} \\  
  \land \\
\Big( q({v_q}_1)^{(l_1,w_1)} \in_{q} (t_3-t) \land q({v_q}_2)^{(l_2,w_2)} \in_{q} (t_3-t_1) \\ \implies  \exists v \in \codom(q({v_q}_1)), m_3', t_3', w_3'.  \\
 \config{m_1[v/x], {c_2}, t_1++[q({v_q}_1)^{(l_1,w_1)}], w_1} \rightarrow^{*} \config{m_3', \eskip, t_3', w_3'} \\ \land (q({v_q}_2)^{(l_2,w_2)}) \not \in_{q} (t_3'-t_1)
\Big)\\
\land \\
\Big(q({v_q}_1)^{(l_1,w_1)} \in_{q} (t_3-t) \land q({v_q}_2)^{(l_2,w_2)} \not\in_{q} (t_3-t_1) \\ \implies  \exists v \in \codom(q({v_q}_1)),  m_3', t_3', w_3'. \\
 \config{m_1[v/x], {c_2}, t_1++[q({v_q}_1)^{(l_1,w_1)}], w_1} \rightarrow^{*} \config{m_3', \eskip, t_3', w_3'} \\ \land (q({v_q}_2)^{(l_2,w_2)})  \in_{q} (t_3'-t_1)
\Big)
\end{array} \right )
\end{array}
\]
\end{defn}
%
Based on the \emph{may-dependency} between the two queries above,
below is their formal definition of query-based dependency graph. 
For every execution of a program $c$ staring with a certain memory and while map
%  configurations, 
they construct a corresponding dependency graph.  
% graph definition
\begin{defn}[Query-based Dependency Graph]
Given a program $c$, a database $D$, a starting memory $m$, an initial loop map $w$, the query-based dependency graph $G(c,D,m,w) = (V, E)$ is defined as: \\
$V =\{q({v_q})^{l,w} \in \mathcal{AQ} \mid \forall t. \exists m',  w', t'.  \config{m ,c, t, w}  \to^{*}  \config{m' , \eskip, t', w' }  \land q({v_q})^{l,w} \in {(t'-t)}  \}$.
\\
$E = \left\{(q({v_q})^{(l,w)},q({v_q}')^{(l',w')}) \in \mathcal{AQ} \times \mathcal{AQ} 
~ \left \vert ~ \mathsf{DEP}(q({v_q}')^{(l',w')},q({v_q})^{(l,w)}, c,w,m,D)
 \right.\right\}$.
\end{defn}
%
% The function $\mathsf{To}(q(v')^{(l',w')}, q(v)^{(l,w)}$ tells that the query request $q(v')^{(l',w')}$ appears after the query request $q(v)^{(l,w)}$ in the trace, by comparing the annotation $(l',w')$ and $(l,w)$. It helps to decide on the direction of one edge.
The edge is directed, when an annotated query $q({v_q})^{(l,w)}$ may depend on its previous query $q({v_q}')^{(l',w')}$, we have the directed
edge $(q({v_q})^{(l,w)}, q({v_q}')^{(l'.w')})$, from $q({v_q})^{(l,w)} $ to $q({v_q}')^{(l'.w')}$.

The query-based dependency graph only considers the newly generated annotated queries during the execution of the program $c$,
so they see the nodes coming from the trace $t'-t$.
The previous trace before the execution of $c$ is excluded when constructing the graph.
% To summarize, for every execution of a program $c$ staring with different configurations, 
% they can construct a corresponding dependency graph. 

\subsection*{Adaptivity Formalization}
Below is the definition of adaptivity from Thesis~\cite{weihao22}, by means of the query-based dependency graph. 
\begin{defn}[Adaptivity in {loop} language]
Given a program $c$, and a memory $m$, a database $D$, a starting loop map $w$, the adaptivity of the dependency graph $G(c, D,m,w) = (V, E)$ is the length of the longest path in this graph. We denote the path from $q({v_q})^{(l,w)}$ to $q({v_q}')^{(l',w')}$ as $p(q({v_q})^{(l,w)}, q({v_q}')^{(l',w')} )$. The adaptivity denoted as $A(c, D, m, w)$.
%
$$A(c, D, m, w) = \max\limits_{q({v_q})^{(l,w)},q({v_q}')^{(l',w')} \in V } |p(q({v_q})^{(l,w)}, q({v_q}')^{(l',w')} )| $$
\end{defn}
\subsection*{Limitations}
Limited by their language design and the dependency graph construction,
this adaptivity definition is weak in the following aspects.
\highlight{
  \begin{enumerate}
    \item \textbf{Expressiveness Limitation}
    \\
    The definition isn't general enough to give the formal adaptivity for the adaptive data analysis programs with non-constant
    while loops.
    However, programs containing while loops of non-deterministic iteration times are very common in adaptive data analysis area.
    This is caused by the expressiveness limitation in their language design and operational semantics design as analyzed
    in Section~\ref{sec:prework-language}.
    \\
    In the following example program similar to the one in Section~\ref{sec:prework-language} with two extra query request commands,
    \[
      {\assign{x}{0}};
      \assign{y}{5};
      \assign{z}{q(x + y)};
      \ewhile (x < y) \edo 
      \{
        \assign{x}{x + 1};
        \assign{y}{y - 1};
        \assign{z}{q(x+y+z)};
        \}\}
      \] 
    the number of iterations cannot be evaluated to a nature number in advance of entering this loop for the same reason. 
      The iteration number is only
    able to be decided during executing this while loop body.
    % This program represents a class of data analysis program with non-constant loop iterations, which is very common in data analysis. However, it isn't supported by their design.
    \\
    Limited by this, they cannot give the adaptivity for this program even though the adaptivity in this program is 4, which is straightforward to observe.
    %  a trace generated for this program
    \item \textbf{Accuracy Limitation}
    \\
    The in-accuracy of this \emph{adaptivity} definition is caused by both of their language design and their graph construction.
    \\
    As analyzed in Section~\ref{sec:prework-language}, the information in non-query requesting variables is lost.
    The dependency passes through these variables is lost, and the adaptivity is lost as well.
    \\
    The other reason for this in-accuracy comes from their graph definition.
    This dependency graph definition relies on a specific memory, while map, and a specific execution trace.
    It limits the adaptivity defined for the adaptive data analysis program has to be w.r.t. one specific
    execution.
    In the other words, this adaptivity definition doesn't correspond to the \emph{adaptivity} for this program,
    but for the program in a certain execution.
    % to The trace only tracks the query requests. This lost the information of the variables
    % which are assigned by query values even they are not assigned by query requests. 
    \item \textbf{Efficiency Limitation}
    \\
    This definition is in-efficient in the senses that it requires the fully unfolding of every iteration for the while loop.
    There are two reasons for this unfolding operation.
    The first one comes from the low-efficiency of their trace-based operational semantics,
    which requires the trace to track the loop iteration number in the annotated query.
    The other comes from their dependency graph generation, which requires every query requests evaluated during the program execution
    as the graph nodes.
    Both of the two processes generate unnecessary and duplicate nodes during the while iterations.
    %  annotatation of the  the query request executed in the program
    % with integer indicating the while loops. 
\end{enumerate}
}