% \subsection{Reachability-Bound Problem \todo{60\% ==> Refine and Entrich}}
% \label{sec:reachability-back}
% \wq{Reachability has wide applications in program analysis. 
% For instance, in security program analysis area, 
% static analysis tool "Zoncolan" finds security issues in Meta's codebase by monitoring any sensitive user data reaching any third-party code.
% In liveness analysis, reachability is used to statically analyze whether some pieces of code will be executed. 
% In data analysis area, reachability-based program analysis can tell data analysts whether certain query uses the results of some other queries.
% As we may already observe, the reachability-based program analysis can answer the question of "whether or not" a program has some property,
% but has troubles in describing "the degree" of the property. 
% In our previous example, our data analysts use program analysis and knows some query relies on others in their programs. 
% However, to improve their data analysis programs, 
% they also want to know "the degree" of the reliance between queries: a query which relies on two other queries relies more 
% "intensely" than another one which only uses the result of one other query.
% }
% \highlight{The number of times a given control location 
% inside a procedure is visited during the program execution
% is one of the importance quantitative reachability properties for programs.
% Finding a tight bound on this quantitative reachability property is
% useful in different applications, such as
% bounding 
% resources consumed by a program such as time, memory,
% network-traffic, power, 
% or helping to estimate other quantitative properties (as opposed to boolean properties)
% of data in programs, such as information leakage or uncertainty propagation.
% In this part, I focus on analyzing this property and propose a new algorithm.
% This algorithm can estimate an upper bound on the number of execution times on a given control location in a program.
% }
\highlight{
%  performs from different aspects.
% }% The reachability-bound problem is
% the problem of finding a symbolic worst-case bound on the number of times a given control location 
% inside a procedure is visited in terms of the inputs to that procedure.
% This concept is first proposed in \cite{GulwaniZ10}, to help to bound the
% % This execution property has broad
% % applications in bounding 
% resources consumed by a program such as time, memory,
% network-traffic, power, 
% or help to estimate some quantitative properties (as opposed to boolean properties)
% of data in programs, such as information leakage or uncertainty propagation.
% Skeleton and Plan: Background and Importance of analyzing the reachability bound.
% \\
% \textbf{Where it is required? How useful it can be? What impact it can bring?}
% \\
% \highlight{
    % In many program analysis areas, solving this problem is important in helping give a precise analysis result.
% For example, in the data analysis area as in PART I, the reachability-bound on each location helps
% in giving a precise bound on the adaptive data analysis program's adaptivity quantity through static analysis.
The execution properties of the program running on the mobile devices affects our daily life from many perspectives.
For example,
from the privacy and security perspective,
%  protection area,
how much secret information is leaked by a program depends on the number of times a certain operation that leaks the data,
% either by direct or indirect information flow, 
is executed~\cite{Malacaria07};
% In the privacy
%  protection area, 
the amount of perturbation in the output data values resulting
from a small perturbation or uncertainty in the input,
values depend on the number of times additive error propagation operators are applied; etc.
% This is the quantitative version of the boolean problem of continuity studied in~\cite{ChaudhuriGL10}. 
Estimating such quantitative properties again requires us to know
%  addressing a similar question as above:
how many times is a given control location inside the program that performs certain operations executed.
% \\
From the performance perspective, it is important to give a precise estimation
on the program's resource cost bound w.r.t. the program's inputs.
For example, in memory-constrained environments such as embedded systems,
it is important to bound the amount of memory required to run certain applications.
In real-time systems, it is important to bound the worst-case execution time of the program.
Applications running on low-power devices or low-bandwidth environments must use up little power or bandwidth respectively. 
With the advent of cloud computing, where users would be charged per program execution,
predicting resource usage characteristics would be a crucial component of accurate bid placement by cloud providers. 
One of the challenges in bounding this cost precisely is that the resource consumption is location-sensitive.
In other words, different location has different resource cost as well as different execution times.
To give accurate estimation results on these execution properties,
% This brings me to one of 
the fundamental questions that need to be addressed 
%  for computing such resource bounds:
is estimating the bound on the execution times
% How many times is 
a given control location inside the program that consumes these resources.
To these reasons, I'm interested in analyzing the bound on the execution times of a program's given control location.
This bound is referred as the reachability-bound in the program analysis area,
which is firstly proposed by the paper~\cite{GulwaniZ10}.
% Motivated by this, this part aims to 
In this paper, finding a symbolic worst-case bound on this quantitative reachability property
in terms of the inputs to that procedure,
is defined as the \emph{reachability-bound problem}.
% This name is firstly proposed by the paper~\cite{GulwaniZ10},
% and s
% Solving this problem is very helpful in improving the program analysis results in different areas.
% i.e., solving the reachability-bound problem.
%   quantitative reachability property
% and provide an accurate solution for the reachability-bound problem.
}
% This is 
% \\
% \textbf{In some other areas, II, III or ...}
% How many times is a given control location inside the program that performs certain operations executed?
% \\
% \textbf{Short Summary} of existing works and limitations
% \\
% \textbf{Short Summary} of the new technique/algorithm: major steps/technique used, major outcome
% \\
% \textbf{Introduce} each step of the new technique/algorithm:
% \\
% Motivated by the importance above,
% the paper \cite{GulwaniZ10} brought up the reachability-bound problem as
% finding a symbolic worst-case bound on the number of times a given control location 
% inside a procedure is visited in terms of the inputs to that procedure.
% \subsection{Motivations \todo{30\% ==> Enrich}}
% \label{sec:reachability-motivation}
% \textbf{Introduce} new technique/ results or experimental results. 
% Summary of comparison with existing works. \cite{GulwaniJK09} \cite{Sumit2010rechability}, \cite{sinn2017complexity}
 % \cite{GulwaniZ10, SinnZV17,GulwaniJK09, GulwaniMC09, abs-2203-04243}. 

\highlight{
Providing a good solution to this problem is challenging.
 In the paper \cite{GulwaniZ10} that introduces this concept,
 they give a two-steps solution by combining the abstract interpretation-based iterative technique
 and the non-iterative proof-rules-based technique.
 However, their solution
%  doesn't solve the reachability
%  bound in a path-sensitive manner.
does not solve this problem in a path-sensitive manner.
It over-approximates the reachability-bound on different paths inside a while loop.
%  \\
 There are also many works in the program complexity analysis and cost analysis area
 \cite{GustafssonEL05, HumenbergerJK18}, 
 \cite{BrockschmidtEFFG16,AlbertAGP08,AliasDFG10,Flores-MontoyaH14} inferring the tight bound
 on program's overall complexity or resource cost.
But their analysis
focus only on estimating the overall complexity 
by either inferring the loop iteration bounds,
 or computing the worst-case running time.
 None of them solve the reachability-bound problem directly or path-sensitively.
To leverage these limitations,
I plan to design a path-sensitive reachability-bound analysis in this section.
 This analysis aims to solve the 
 reachability-bounds problem path-sensitively.
 % for every labeled command taking the different paths inside while loop into consideration.
It has three parts as follows,
%  similar to the program analysis framework for adaptivity in PART I.
 \begin{enumerate}
 \item A standard while language with trace-based operational semantics is presented in Section~\ref{sec:reachability-language}.
 \item The definition for the program's reachability-bound is presented in Section~\ref{sec:reachability-exe}.
 \item A path-sensitive reachability-bounds algorithm is presented in Section~\ref{sec:reachability-static}.
 \end{enumerate}}
% \subsection{Outline}
% \label{sec:reachability-outline}
% The rest parts of this section is organized as follows. 
% \begin{enumerate}
% \item The previous works on adaptive data analysis are introduced in Section~\ref{sec:prework}.
% \item The proposed new program analysis framework for the adaptivity of Adaptive Data Analysis is presented 
% in Section~\ref{sec:adapt-analysis}.
% This new program analysis framework has three major components:
% \begin{enumerate}
% \item A while-like language extended with query request feature, named {\tt Query While} Language, 
% used to implement the adaptive data analysis in Section~\ref{sec:adapt-language};
% \item A formal adaptivity model through execution-based adaptivity analysis in Section~\ref{sec:adapt-exe};
% \item A static program analysis algorithm, named {\THESYSTEM} through static adaptivity analysis in Section~\ref{sec:adapt-static}.
% \end{enumerate}
% \end{enumerate}