\documentclass[a4paper,11pt]{article}
\usepackage[table]{xcolor}
\include{prelude}
\include{ldefs}
\newcommand{\THESYSTEM}{\textsf{AdaptFun}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter

\makeatother

\usepackage{babel}
\begin{document}

\title{{\em Dissertation Prospectus}
\\  A Full-Spectrum Program Analysis for Adaptivity of Adaptive Data Analysis, 
\\ with Generalization on Program Resource Cost}

\author{Jiawen Liu\\ Department of Computer Science, Boston University}
\maketitle
\begin{abstract}
\input{chapters/Abstract}
  
\end{abstract}
\tableofcontents{}

\section{Introduction to Adaptivity Analysis}
\label{sec:introduction}
% \include{chapters/introduction}
\cleardoublepage



\section{The Query Language for Adaptive Data Analysis Program}
\label{sec:language}
In this chapter, we formally introduce the language we will focus on for writing data analyses.  
This is a simple loop language with some primitives for calling queries. 
After defining the syntax of the language and showing an example, we will define its trace-based operational semantics. 
This is the main technical ingredient we will use to define the program's adaptivity.

\subsection{Syntax of Query While Language}
\label{sec:language-syntax}
In this section, we formally introduce the language we will focus on for writing data analyses.  This is a standard while language with some primitives for calling queries. After defining the syntax of the language and showing an example, we will define its trace-based operational semantics. This is the main technical ingredient we will use to define the program's adaptivity.
% We will conclude this section by discussing the limitation of this language with respect to static analysis for adaptivity.

\input{chapters/syntax}

\subsection{Trace-based Operational Semantics}
\label{sec:language-os}
\input{chapters/os}
% \input{chapters/language}
\cleardoublepage

\section{The Execution-Based Program Analysis for Adaptivity}
\label{sec:dynamic}
\input{chapters/dynamic}

\section{The Program Static Analysis for Adaptivity}
\label{sec:static}
\input{chapters/static}
\cleardoublepage


\section{Further Features}
\label{sec:furthers}
\input{chapters/furthers}

% \include{chapters/dynamic}
% \cleardoublepage

% \include{chapters/static}
% \cleardoublepage

\section{Status and Plan}
The $\THESYSTEM$ presented in Section~\ref{sec:dynamic} and Section~\ref{sec:static} are submitted as a paper to POPL'2023 and implemented as well. Below is the timeline plan for the further features of this work.
\begin{itemize}
\item September 05, 2022: Finish the improved execution-based dependency depth analysis and implementation
\item September 20, 2022: Finish Path Sensitive Reachability Bound Algorithm Formalization and implementation
\item September 30, 2022: Improve the completeness of the static adaptivity computation algorithm and implementation
\item October 15, 2022:  Finish generalization on program resource cost analysis and implementation
\item November 05, 2022: Finish Path Sensitive Reachability Bound paper writing and Submit to PLDI 2023
\item November 25, 2022: Finish thesis
\item December 05, 2022: Defend
\end{itemize}


\bibliographystyle{plain}
\bibliography{main.bib}

\end{document}
