\section*{Acknowledgments}

I would like to first express my sincerest thanks to Boston University, 
it is a great experience to study, do research, and enjoy my life here. 
I am so lucky that I made my decision to transfer to Boston University during the summer of 2019. 
I like the seminars, like the classes, like my colleagues here, like the discussion about logic, type systems. 

I have been at BU for more than two years. 
Before that, I stayed at Buffalo for three years. 
Reviewing my path to Ph.D., so many people have helped me. 
In particular, I would like to say thank you so much to my advisor, Professor Marco Gaboardi. 
Thanks for your being an amazing advisor, for your bringing me to BU, for encouraging me to attend conferences, for providing great opportunities to collaborate with great researchers, for teaching me how to become a better human being! 
I am so fortunate that I can work with Marco for these years.

I want to thank my committee members. 
Great thanks to Professor Assaf Kfoury for your kindness in being the chair of my committee.

I would like to thank all my colleagues at Boston University as well as at the University at Buffalo. 
Thanks to Professor Lukasz Ziarek for his help at Buffalo. 
Thanks to all my collaborators in these works in the dissertation.

Last, but by no means least, I want to thank my grandmother Xiuqin Yang, for your support in pursuing my Ph.D. 
I am also thankful to my family members, my father Hui Liu, my mother Yahong Hu and my brother Hu Liu.  
Thanks to my lovely kitty Taro for his company. 

